Solution-aware vs global ReLU ranking: \\ partial MILP strikes back for DNN verification

### 2025-01-25 CAV 2025 TODO/experiments.tex

\begin{figure}[h!]
	\centering
	\vspace*{-0.3cm}
	\includegraphics[height=8cm]{Plot for table 3}.
	\vspace*{-0.4cm}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{ DivideAndSlide} vs random choice.}
	\label{fig_table3}
\end{figure}

@@

Notice that results for other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN. Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd 
of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN. Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em hard} MNIST DNNs at several time-out settings. 
Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible.

>>>>

\begin{figure}[h!]
	\centering
	\vspace*{-0.3cm}
	\includegraphics[height=8cm]{Plot for table 3}.
	\vspace*{-0.4cm}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the (1st and) 2nd layer, chosen by our {\bf Utility} function vs \cite{DivideAndSlide} vs random choice.}
	\label{fig_table3}
\end{figure}

@@

Notice that results for other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN. Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd 
of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN. Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em hard} MNIST DNNs at several time-out settings. 
Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible.
